`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-03-10 paper/paper.qmd
Fix Michael and Aarathy's affiliation

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    corresponding: true
    affiliation: "1"
  - name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
    affiliation: "1"
  - name: Aarathy Babu
    orcid: 0000-0002-6982-5989
    affiliation: "1,3"
  - name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
    affiliation: "1"
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: "1,2"
affiliations:
  - index: 1
    name: The Kids Research Institute Australia, WA, Australia
  - index: 2
    name:  University of Western Australia, WA, Australia
  - index: 3
    name: Monash University, VIC, Australia
date: today
bibliography: paper.bib
---

>>>>

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    corresponding: true
    affiliation: "1"
  - name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
    affiliation: "1"
  - name: Aarathy Babu
    orcid: 0000-0002-6982-5989
    affiliation: "1"
  - name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
    affiliation: "3"
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: "1,2"
affiliations:
  - index: 1
    name: The Kids Research Institute Australia, WA, Australia
  - index: 2
    name:  University of Western Australia, WA, Australia
  - index: 3
    name: Department of Econometrics and Business Statistics, Monash University, VIC, Australia
date: today
bibliography: paper.bib
---
